BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2016-01-27 Paper/BOAST.tex
Added Acknowledgments.
Tentative abstract and improved conclusion.

\newcommand{\code}[1]{\texttt{#1}}

@@

\address[lig]{Laboratoire d'Informatique de Grenoble}
\address[cnrs]{Centre National de la Recherche Scientifique}
\address[cea]{CEA/INAC/SP2M/L\_Sim}
\address[ujf]{Université Joseph Fourier}
\address[inria]{Inria}
\begin{abstract}
The Abstract.
\end{abstract}

@@

In this paper we presented the BOAST infrastructure as well as its
application to three use cases from the Mont-Blanc project. Results are
encouraging as BOAST proved to be a powerful and flexible tool that allowed
gains in performance and performance portability.

Future development will focus on three goals. Interfacing with binary analysis
tools like MAQAO~\cite{djoudi2005exploring} in order to build a feedback loop to
guide optimization. Interfacing with search space modellers/pruners in order to
optimize the search of the optimal version of a kernel. Continue working on
vector code. For instance producing a collection of small to medium useful
vector patterns (transposition, for instance) in BOAST could really help develop
vectorized version of our algorithm.

>>>>

\newcommand{\code}[1]{\texttt{#1}}
\newcommand*{\Num}{N\textsuperscript{o}\xspace}

@@

\address[lig]{Laboratoire d'Informatique de Grenoble}
\address[cnrs]{Centre National de la Recherche Scientifique}
\address[cea]{CEA/INAC/SP2M/L\_Sim}
\address[ujf]{Université Joseph Fourier}
\address[inria]{Inria}
\begin{abstract}
The portability of real HPC applications on new platforms is an open and very
delicate problem.  Especially the performance portability of the underlying
computing kernels, is problematic as they need to be tuned for each and every
platform the application encounters.  This paper presents BOAST, a
metaprogramming framework dedicated computing kernels.  BOAST allows the
description of a kernel and its possible optimizations using a DSL.  BOAST
runtime will then compare the different version's performance as well as verify
their exactness. BOAST is applied to three use cases: a Laplace kernel in
OpenCL, and two HPC applications BigDFT (electronic density computation) and
SPECFEM3D (seismic and wave propagation).
\end{abstract}

@@

In this paper we presented the BOAST infrastructure as well as its application
to three use cases from the Mont-Blanc project. Results are encouraging as
BOAST proved to be a powerful and flexible tool that allowed gains in
performance compared to hand tuned codes. Performance portability of those
codes is also improved.

Future development will focus on three goals. Interfacing with binary analysis
tools like MAQAO~\cite{djoudi2005exploring} in order to build a feedback loop
to guide optimization. Interfacing with search space modellers/pruners in order
to optimize the search of the optimal version of a kernel. Work should also
continue on improving the support for vector codes. For instance producing a
collection of small to medium useful vector patterns (transposition, for
instance) in BOAST could really help users develop vectorized version of their
algorithm.

\section*{Acknowledgments}

The research leading to these results has received funding from the European
Community's Seventh Framework Programme [FP7/2007-2013] under grant agreement
\Num 288777 and 610402.
